COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-08-24 main.tex
Add first few figures

\documentclass[twocolumn]{aastex62}
\usepackage{natbib}
\usepackage[colorinlistoftodos]{todonotes}
%\usepackage{academicons}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{apj}

@@

@@

@@

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/test.eps}
    \caption{Caption goes here.
    \label{fig:test}}
\end{figure}

>>>>

\documentclass[twocolumn]{aastex63}
\usepackage{natbib}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{aasjournal}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/rtheta.png}
    \caption{Caption goes here.\label{fig:rtheta}}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/ae.png}
    \caption{Caption goes here.\label{fig:ae}}
\end{figure*}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/long_ph.png}
    \caption{Caption goes here.\label{fig:long_ph}}
\end{figure}

@@

Outline for this section:
\begin{itemize}
\item Time evolution of disk surface density for circ and ecc
\item Time evolution of sma vs ecc
\item Number of collisions as a function of sma and radial distance
\item Number of collisions as a function of mean anomaly and delta mean anomaly
\item Comparison between safronov rate and actual collision statistics
\end{itemize}

@@

\begin{itemize}
\item Show CASA images
\end{itemize}

@@
